Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-09 chapters/introduction/introduction.tex
new section for feature learning

>>>>

Automatic feature engineering has drawn a lot of attention over the
past years in the computer vision community due to its efficiency and
not requiring expert knowledge about the data.  In recent years, deep
neural networks are acknowledged as good tools to learn high-level
features for image understanding.  As parametric algorithms, deep
neural networks require training for their parameters.  Methods to
train deep neural networks include supervised algorithms, unsupervised
algorithms, and reinforcement learning. Supervised algorithms are the
most popular and commonly applied in many computer vision areas,
thanks to their good performances and the fact that they are easy to
implement. However, supervised learning approaches are sensitive to
the quality of data annotations. In some applications like overhead
image segmentation and transient attributes estimation, data with
noise-free annotation is either very limited in quantity or
technically difficult to acquire.  In this thesis, Our methods focus
on lavaging the camera geographic information to deal with the
challenges of lacking noise-free annotations during DNN training. The
insight is that the camera geographic information encodes the semantic
information because it is related to the appearances of the scenes.
